Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections at the LArIAT experiment

### 2018-06-01 Chapter-3/3-TheLArIATExperiment.tex
s

\subsection{LArTPC: Light Collection System}\label{sec:TPCLight} 
The collection of scintillation photons is the second mechanism of particle detection in argon other than the ionization electrons. Over the course of LArIAT's three years of data taking, the light collection system changed several times. We describe here the light collection system for Run II. Two PMTs, a 3-inch diameter Hamamatsu R-11065 and 2-inch diameter ETL D757KFL~\cite{lightsys-pmttests}, as well as three SiPMs arrays (two Hamamatsu S11828-3344M 4x4 arrays and one single-channel SensL MicroFB-60035) are mounted on the PEEK support structure. PEEK screws into an access flange as shown in Figure~\ref{lightsys_pmts}, on the anode side, leaving  approximately 5~cm of clearance from the collection plane.

>>>>

\subsection{LArTPC: Light Collection}\label{sec:TPCLight} 
The collection of scintillation photons is the second mechanism of particle detection in argon other than the ionization electrons. Over the course of LArIAT's three years of data taking, the light collection system changed several times. We describe here the light collection system for Run II. Two PMTs, a 3-inch diameter Hamamatsu R-11065 and 2-inch diameter ETL D757KFL~\cite{lightsys-pmttests}, as well as three SiPMs arrays (two Hamamatsu S11828-3344M 4x4 arrays and one single-channel SensL MicroFB-60035) are mounted on the PEEK support structure. PEEK screws into an access flange as shown in Figure~\ref{lightsys_pmts}, on the anode side, leaving  approximately 5~cm of clearance from the collection plane.
